First estimate of a galaxy rotational velocity from its observed Lyman-$\alpha$ line

### 2015-04-17 paper/ms.tex
basic format and text

%Document Class
\documentclass{latex/emulateapj}
\usepackage{multirow,color,wrapfig,ulem}

%Packages and Commands
\include{latex/packages_commands}

\begin{document}

\title{Titulo}
\shorttitle{shorttitle}

\shortauthors{shortauthors}

\author{author1, author2 \& author3} 
\affil{Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
No. 18A-10, Edificio Ip, Bogot\'a, Colombia}

\email{email1}
\email{email2}
\email{email3}

\keywords{keywords....}

\begin{abstract}

Abstract...

\end{abstract}

@@

Introduction... \\

@@

@@

\bibliographystyle{latex/apj}
\bibliography{references}

\newpage

>>>>

\documentclass{emulateapj}
\submitted{{\it Submitted for publication in ApJ Letters}}
\usepackage{multirow,color,wrapfig,ulem}
\usepackage {graphicx}
\usepackage{graphics}
\usepackage[dvips]{epsfig}
\newcommand{\avg}[1]{\langle{#1}\rangle}  
\newcommand{\nscatt}{\langle N_{\rm  scatt}\rangle}
\newcommand{\ly}{{\ifmmode{{\rm Ly}\alpha~}\else{Ly$\alpha$~}\fi}}
\newcommand{\hMpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}   
\newcommand{\hGpc}{{\ifmmode{h^{-1}{\rm Gpc}}\else{$h^{-1}$Gpc }\fi}}   
\newcommand{\hmpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}  
\newcommand{\hkpc}{{\ifmmode{h^{-1}{\rm kpc}}\else{$h^{-1}$kpc }\fi}}  
\newcommand{\hMsun}{{\ifmmode{h^{-1}{\rm
        {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}   
\newcommand{\hmsun}{{\ifmmode{h^{-1}{\rm
        {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}   
\newcommand{\Msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
\newcommand{\msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
\newcommand{\lya}{{Lyman $\alpha$~}}
\newcommand{\clara}{{\texttt{CLARA}}~}
\newcommand{\rand}{{\ifmmode{{\mathcal{R}}}\else{${\mathcal{R}}$ }\fi}}  
\newcommand{\hs}{{\hspace{1mm}}}  
\newcommand{\kms}{{\ifmmode{{\mathrm{\,km\ s}^{-1}}}\else{\,km~s$^{-1}$}\fi}}
% definition to produce a "less than or similar to" symbol
\def\lsim{~\rlap{$<$}{\lower 1.0ex\hbox{$\sim$}}}
% definition to produce a "greater than or similar to" symbol
\def\gsim{~\rlap{$>$}{\lower 1.0ex\hbox{$\sim$}}}
%@arxiver{fig3.pdf,fig11a.pdf, fig11b.pdf} 
\begin{document}

\title{First estimate of a galaxy rotational velocity from
  its observed Lyman-$\alpha$ line} 
\shorttitle{Rotational velocity from the Lyman $\alpha$ line}

\shortauthors{Remolina-Gutierrez, Garavito-Camargo, Forero-Romero}

\author{ Maria C. Remolina-Gutierrez, Juan N. Garavito-Camargo, Jaime
  E. Forero-Romero}  
\affil{Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
No. 18A-10, Edificio Ip, Bogot\'a, Colombia}
\email{mc.remolina197@uniandes.edu.co}
\email{jn.garavito57@uniandes.edu.co}
\email{je.forero@uniandes.edu.co}

\keywords{galaxies: high-redshift --- line: formation --- methods:
  numerical ---  radiative transfer} 
\begin{abstract}
First.
\end{abstract}

@@

Introduction... \\ 
\cite{Garavito14}

@@

\begin{figure}
\begin{center}
  \includegraphics[width=0.5\textwidth]{mcmc.png}
\end{center}
\caption{
    \label{fig:mcmc_result}}  
\end{figure}

\begin{figure*}
\begin{center}
  \includegraphics[width=0.7\textwidth]{parameters.png}
\end{center}
\caption{
    \label{fig:mcmc_triangle}}  
\end{figure*}

@@

\bibliographystyle{apj}
\bibliography{references}

\end{document}
